---
title: 'Anomaly Detection in Real-Time Data with General Adversarial Network (GAN)'
date: ''
format: 
  baylor_theme-revealjs:
    author: 'Nathen Byford'
    footer: 'Nathen Byford'
---

```{r}
#| include: false

library("tidyverse"); theme_set(theme_minimal())
```


## Contents

1. Motivation and goals
2. Methods
3. Data


# Motivation and Goals

## Motivation {.smaller}

real-time or streaming data analysis is the backbone of modern data-driven decision-making. A key part of utilizing real-time data is having clean data.

> Garbage in, garbage out.

In time series processes that are observed in real time it is even more important to be able to detect anomalies so that the cause can be identified.

Anomalies can be caused by:

* Faulty sensor
* Poor data quality
* External factors
* Adversarial Attacks

## Goals

There are many methods being used to detect anomalies in streaming data with data driven methods. Typically clustering algorithems, time series analysis, change point detection, and even statistical tests. 

::: def
My goal is to utilize General Adversarial Network (GAN) models to detect anomalies on the Numenta Anomaly Benchmark (NAB) data set.
:::

# Methods

# Data

## Numenta Anomaly Benchmark



## EDA

```{r}
#| message: false

data <- read_csv("data/combined_data.csv")

data |> ggplot(aes(x = timestamp, y = value)) +
  geom_line(aes(color = company), alpha = .6) +
  geom_point(data = filter(data, anomaly), shape = 23) +
  facet_wrap(vars(company), scales = "free_y") +
  scale_color_viridis_d(option = "H") +
  labs(title = "Time plot of Twitter tags with anomalies",
       x = "Time", y = "Twitter tags") +
  theme(legend.position = "none")
```

:::aside
CRM is salesforce, and KO is Coca-Cola
:::